\documentclass[a4paper,11pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\setlength{\parindent}{0pt}
\renewcommand{\baselinestretch}{1.1}

%-------------------- HEADER --------------------
\begin{document}
\begin{center}
{\LARGE \textbf{Manjeet Singh}} \\[4pt]
Email: manjeetsingh802152@gmail.com \quad | \quad Phone: +91 6203830865 \\[2pt]
LinkedIn: linkedin.com/in/manjeetsingh \quad | \quad GitHub: github.com/manjeetsingh354
\end{center}
\vspace{0.5cm}

%-------------------- CAREER OBJECTIVE --------------------
\section*{Career Objective}
Aspiring Software Developer and Full-Stack Engineer with hands-on experience in MERN stack, problem-solving, and modern software practices. Seeking opportunities to contribute technical skills and grow within innovative organizations.

%-------------------- EDUCATION --------------------
\section*{Education}
\begin{itemize}[leftmargin=*]
  \item \textbf{B.Tech in Computer Science \& Engineering}, Durgapur Institute of Advanced Technology and Management \hfill 2022--2026
  \item \textbf{12th}, Bihar Board Open Schooling \hfill 2022 \\
  Score: 64\%
  \item \textbf{10th}, Kendriya Vidyalaya \hfill 2017 \\
  Score: 78\%
\end{itemize}

%-------------------- TECHNICAL SKILLS --------------------
\section*{Technical Skills}
\textbf{Programming Languages:} C, Python, C++, Java, Kotlin, JavaScript \\
\textbf{Frontend:} HTML, CSS, JavaScript, React.js \\
\textbf{Backend:} Node.js, Express.js \\
\textbf{Databases:} MongoDB, MySQL, SQL \\
\textbf{DevOps \& Tools:} Git, GitHub, Docker, Kubernetes, CI/CD, Azure, AWS, Cloud Deployment \\
\textbf{Core CS Subjects:} Data Structures \& Algorithms, Computer Networks, Operating Systems

%-------------------- SOFT SKILLS --------------------
\section*{Soft Skills}
Problem-Solving \& Analytical Thinking, Effective Communication, Teamwork \& Collaboration, Adaptability, Time Management, Attention to Detail

%-------------------- PROJECTS --------------------
\section*{Projects}
\begin{itemize}[leftmargin=*]
  \item \textbf{Pathology Website} – Full-stack healthcare management system using MERN stack with responsive UI and database integration.
  \item \textbf{Netflix Clone} – Responsive front-end streaming app prototype using HTML, CSS, and JavaScript.
  \item \textbf{REST API} – RESTful services using Node.js and Express.js with CRUD functionality.
  \item \textbf{To-Do List Manager} – Task management tool applying Object-Oriented Programming concepts.
\end{itemize}

%-------------------- WORK EXPERIENCE --------------------
\section*{Work Experience}
Fresher – Looking for opportunities to apply technical and problem-solving skills.

%-------------------- INTERNSHIPS --------------------
\section*{Internships / Training}
\textbf{Core Java Intern} \hfill Aug 2024 -- Sep 2024 \\
Webflex Consultancy Services Pvt. Ltd. (ISO 9001:2015 Certified)
\begin{itemize}[leftmargin=*]
  \item Completed 4-week internship in Core Java, covering OOP, exception handling, and data structures.
  \item Developed practical coding assignments to enhance problem-solving skills.
\end{itemize}

\textbf{Tata Prashikshan Intern} \hfill Aug 2025 -- Sep 2025 \\
Tata Steel Ltd., Durgapur (Online/Offline)
\begin{itemize}[leftmargin=*]
  \item Selected for Tata Steel’s Tata Prashikshan Internship Program 2025 (Computer Science/IT).
  \item Worked on project-based assignments applying academic concepts to industrial challenges.
  \item Gained exposure to IT systems, corporate practices, and process management.
  \item Strengthened skills in teamwork, problem-solving, and real-world software development.
\end{itemize}

%-------------------- CERTIFICATIONS --------------------
\section*{Certifications}
\begin{itemize}[leftmargin=*]
  \item Full-Stack Development Internship – Tata Steel
  \item Java Programming Certification – Webflex Consultancy Services Pvt. Ltd.
\end{itemize}

%-------------------- LANGUAGES --------------------
\section*{Languages}
English – Fluent \\
Hindi – Native

\end{document}